\propertitle

### 2020-03-17 replies1_ncomp.tex
update

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2020-03-17T01:02:47+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourtrue% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimfalse
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\firstdraft}{16 March 2020}
\newcommand*{\firstpublished}{16 March 2020}
\newcommand*{\updated}{\ifarxiv***\else\today\fi}
\newcommand*{\propertitle}{Sketch of replies to N. Comp. reviews%\\{\large ***}%
}% title uses LARGE; set Large for smaller
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{}
\newcommand*{\pdfauthor}{}
\newcommand*{\headauthor}{}
\newcommand*{\reporthead}{}%\ifarxiv\else Open Science Framework \href{https://doi.org/10.31219/osf.io/***}{\textsc{doi}:10.31219/osf.io/***}\fi}% Report number

@@

We partly agree with the reviewer's concern, but for different reasons. The
simple comparison of the log-evidences is not a problem in itself, as
explained below. The problem is what is meant by \enquote{model} and what
is being compared. Under one interpretation, our calculation of the
log-evidence is missing a factor, which comes from the full Bayesian
analysis. This factor, however, should be roughly the same in the
calculations from the sample and from the larger population, so our point
that the two calculations lead to different conclusions still holds. Under
another interpretation our calculation is correct as it is. We explain this
below.

@@

There are many differing, fragmented views on the questions of comparison,
complexity, nesting, and \enquote{penalization} of models. Our view is
close to that expressed in several works, studies, and commentaries
\footcites[\eg][]{good1950,good1985,kadaneetal1980b,jonesetal1986,chatfield1995,copasetal1995,draper1995,spiegelhalteretal1995,raftery1995,gelmanetal1995,mackay1995_r2003,draperetal1996,hoetingetal1999,clydeetal1999,browneetal2006},
and well-explained in MacKay \citey{mackay1992}. According to this view,
which we summarize below, the log-evidence automatically takes care of
model complexity.

The main question, on the other hand, is what we mean by \enquote{model}.
There are two main possibilities\ibid: model as a family, or model as a specific
distribution.

\textbf{(A)} If by \enquote{model} we mean a family of probability
distributions, \eg\ (apart from normalization)
\[\conds*{\exp\biggl[-\frac{(x-\mu)^{2}}{2\sigma^{2}}\biggr]\,\di x}{
    \mu\in\RR, \sigma \in \RR_{>0}}\;,\]
then model comparison is ill-defined. % Each distribution in the family
% assigns a different probability, and it is not clear which should be
% chosen or how they should be combined and why.
It may happen that the optimal distribution in family $\mathcal{F}_{1}$
assigns more probability to the observed data than the optimal distribution
in family $\mathcal{F}_{2}$, and yet $\mathcal{F}_{1}$ assigns \enquote{on
  average} lower probabilities to the data than $\mathcal{F}_{2}$. It is
not clear how the two families should be compared in this case, or what
$\p(D \| \mathcal{F}_{i})$ is. A hypothesis is ill-defined, or at least
useless, if it does not allow us to assign a probability to the data. Such
a probability can be obtained if we specify a pre-data probability
distribution over the distributions in the family, \eg\
$\pf(\mu,\sigma \| I)\,\di\mu\,\di\sigma$ in the example above.
\enquote{Model} must therefore be redefined as a family of distributions
\emph{and} a pre-data distribution over such family
\citep{dawid1982,dawid1993}; under exchangeability, this is mathematically
equivalent to the definition (B) below
\citep[\chap~4]{bernardoetal1994_r2000}. This redefinition has several
consequences:

First, two models are different if they have the same family but different
distributions over it. In fact they clearly lead to different probabilities
on the data space. Two such models are also mutually exclusive,
$\p(M_{1} \land M_{2} \|I)=0$, because we cannot use $M_{1}$'s family
distribution \emph{and} $M_{2}$'s family distribution at the same time.
It's either-or. This consequence makes sense from a nonparametric
perspective, where a parametric model is just a delta-like nonparametric
distribution, concentrated on a lower-dimensional manifold (the family
above) of the full space of distributions \citep[p.~761]{draperetal1996}.
The notion of nested models becomes unimportant from this perspective.
Some authors try to define some \enquote{standard} distribution associated
to a family, but we agree with those \citep[\eg][]{copasetal1979}[DeGroot
in][]{lindleyetal1982} who find such definitions ultimately arbitrary. Many
such distributions lead, moreover, to mathematical singularities.

@@

\textbf{(B)} If by \enquote{model} we mean a specific distribution, \eg\
\[ \exp\biggl[-\frac{(x-5)^{2}}{18}\biggr]\,\di x \;,\] then two models can
of course be directly compared: $\p(D \|M_{i}, I)$ is well-defined. In this
case the \enquote{dimensionality} of the model is undefined, however. The
distribution above could be considered as belonging to the family
$\set[\Big]{\exp\Bigl[-\frac{(x-\mu)^{2}}{18}\Bigr]}$, or
$\set[\Big]{\exp\Bigl[-\frac{(x-5)^{2}}{2\sigma^{2}}\Bigr]}$, or
$\set[\big]{\exp[f(x-5)]}$, and so on. A point in a manifold belongs to an
infinity of submanifolds.

Yet, the property of having a minimal sufficient statistic is still
well-defined for a model in this sense, in an exchangeable context. The
model above has $\set[\big]{n, \widebar{x}, \widebar{x^{2}}}$ (or any
equivalent set) as minimal sufficient statistics, where the bar denotes the
sample average. Thus two models having different sufficient statistics can
be compared without reference to any family. Interpreted in this sense our
calculations of \sect~4 are correct.

The question, in summary, is what exactly is being compared, whether
families (and what their accompanying distributions are) or single
distributions. The literature is unclear and contradictory on this. But, in
either case, our calculations show that the approaches based on a
population and a sample thereof can lead to different conclusions -- in
accordance with the non-preservation of sufficiency under sampling -- and
they provide a way to bypass this problem.

>>>>

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2020-03-17T02:31:16+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourtrue% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimfalse
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\firstdraft}{16 March 2020}
\newcommand*{\firstpublished}{16 March 2020}
\newcommand*{\updated}{\ifarxiv***\else\today\fi}
\newcommand*{\propertitle}{Sketch of replies to N. Comp. reviews%\\{\large ***}%
}% title uses LARGE; set Large for smaller
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{}
\newcommand*{\pdfauthor}{}
\newcommand*{\headauthor}{}
\newcommand*{\reporthead}{}%\ifarxiv\else Open Science Framework \href{https://doi.org/10.31219/osf.io/***}{\textsc{doi}:10.31219/osf.io/***}\fi}% Report number

@@

We partly agree with the reviewer's concern, but for different reasons. The
simple comparison of the log-evidences is not a problem in itself, as
explained below. % The problem is what is meant by \enquote{model} and what
% is being compared. Under one interpretation,
Our calculation of the log-evidence is missing a factor, which comes from
the full Bayesian analysis. This factor, however, should be roughly the
same in the calculations from the sample and from the larger population, so
our point that the two calculations lead to different conclusions still
holds. Under another interpretation our calculation is correct as it is. We
explain this below.

@@

There are many differing, fragmented views on the questions of comparison,
complexity, nesting, and \enquote{penalization} of models. Our view is
close to that expressed in several works, studies, and commentaries
\footcites[\eg][]{good1950,good1985,kadaneetal1980b,jonesetal1986,chatfield1995,copasetal1995,draper1995,spiegelhalteretal1995,raftery1995,gelmanetal1995,mackay1995_r2003,draperetal1996,hoetingetal1999,clydeetal1999,browneetal2006},
and well-explained in MacKay \citey{mackay1992}. According to this view,
which we summarize below, the log-evidence automatically takes care of
model complexity. This view hinges on a clear definition of what a
\enquote{model} is.

If by \enquote{model} we mean a family of probability distributions, \eg\
(apart from normalization)
\[\conds*{\exp\biggl[-\frac{(x-\mu)^{2}}{2\sigma^{2}}\biggr]\,\di x}{
    \mu\in\RR, \sigma \in \RR_{>0}}\;,\]
then model comparison is ill-defined. % Each distribution in the family
% assigns a different probability, and it is not clear which should be
% chosen or how they should be combined and why.
It may happen that the optimal distribution in family $\mathcal{F}_{1}$
assigns more probability to the observed data than the optimal distribution
in family $\mathcal{F}_{2}$, and yet $\mathcal{F}_{1}$ assigns \enquote{on
  average} lower probabilities to the data than $\mathcal{F}_{2}$. It is
not clear how the two families should be compared in this case, or what
$\p(D \| \mathcal{F}_{i})$ is. A hypothesis is ill-defined, or at least
useless, if it does not allow us to assign a probability to the data. Such
a probability can be obtained if we specify a pre-data probability
distribution over the distributions in the family, \eg\
$\pf(\mu,\sigma \| I)\,\di\mu\,\di\sigma$ in the example above.
\enquote{Model} must be therefore redefined as a family of distributions
\emph{and} a pre-data distribution over such family
\citep{dawid1982,dawid1993}. This redefinition also turns out to be
equivalent, under exchangeability, to the specification of a single
predictive distribution, that is, a joint probability for any number of
samples
\citep[\chap~4]{bernardoetal1994_r2000}{fortinietal2000,ressel1983_r1985,lauritzen1984}.
This redefinition has several consequences:

First, two models are different if they have the same family but different
distributions over it. In fact they clearly lead to different predictive
probabilities on the data space. Two such models are also mutually
exclusive, $\p(M_{1} \land M_{2} \|I)=0$, because we cannot use $M_{1}$'s
family distribution \emph{and} $M_{2}$'s family distribution at the same
time. It's either-or. This consequence makes sense from a nonparametric
perspective, where a parametric model is just a delta-like nonparametric
distribution, concentrated on a lower-dimensional manifold (the family
above) of the full space of distributions \citep[p.~761]{draperetal1996}.
The notion of nested models becomes unimportant from this perspective. Some
authors try to define some \enquote{standard} distribution associated to a
family, but we agree with those \citep[\eg][]{copasetal1979}[DeGroot
in][]{lindleyetal1982} who find such definitions ultimately arbitrary. Many
such distributions lead, moreover, to mathematical singularities.

@@

% \medskip

% \textbf{(B)} If by \enquote{model} we mean a specific distribution, \eg\
% \[ \exp\biggl[-\frac{(x-5)^{2}}{18}\biggr]\,\di x \;,\] then two models can
% of course be directly compared: $\p(D \|M_{i}, I)$ is well-defined. In this
% case the \enquote{dimensionality} of the model is undefined, however. The
% distribution above could be considered as belonging to the family
% $\set[\Big]{\exp\Bigl[-\frac{(x-\mu)^{2}}{18}\Bigr]}$, or
% $\set[\Big]{\exp\Bigl[-\frac{(x-5)^{2}}{2\sigma^{2}}\Bigr]}$, or
% $\set[\big]{\exp[f(x-5)]}$, and so on. A point in a manifold belongs to an
% infinity of submanifolds.

% Yet, the property of having a minimal sufficient statistic is still
% well-defined for a model in this sense, in an exchangeable context. The
% model above has $\set[\big]{n, \widebar{x}, \widebar{x^{2}}}$ (or any
% equivalent set) as minimal sufficient statistics, where the bar denotes the
% sample average. Thus two models having different sufficient statistics can
% be compared without reference to any family. Interpreted in this sense our
% calculations of \sect~4 are correct.

% \medskip

% The question, in summary, is what exactly is being compared, whether
% families (and what their accompanying distributions are) or single
% distributions. The literature is unclear and contradictory on this. But, in
% either case, our calculations show that the approaches based on a
% population and a sample thereof can lead to different conclusions -- in
% accordance with the non-preservation of sufficiency under sampling -- and
% they provide a way to bypass this problem.
